Cross Validation Approaches for Penalized Cox Regression

### 2019-02-27 main.tex
Edits to 3.1

@@

%%%%%%%%%%%%%
%%%%%%%%%%%%%
\section{Methods}
%%%%%%%%%%%%%
%%%%%%%%%%%%%

@@

To address this issue, \citet{Verweij1993} proposed an alternative method for cross-validation in Cox models:
\begin{equation}
\label{eq:VVH}
	\CVE = -\sum_{k = 1}^K \left\{ \ell(\hat{\beta}^{- k})  - \ell^{-k}(\hat{\beta}^{- k}) \right\}. 
\end{equation}
\bnote{we should add 2 here as well to be consistent with the notation in previous paragraph?}
Here, $\ell(\hat{\beta}^{-k})$ is the log partial likelihood evaluated at $\hat{\beta}^{-k}$ using the entire data set $D$ and $\ell^{-k}(\hat{\beta}^{-k})$ is the log partial likelihood evaluated at $\hat{\beta}^{-k}$ on %\note{FIX!}
the training set $T_k$. There should be enough observations in $T_k$ to build up the risk set as long as the entire data has a reasonable sample size. We refer to this cross-validation method as the Verweij and Van Houwelingen (V\&VH) approach. For many models, such as logistic regression or linear regression, these quantities $\ell(\hat{\beta}^{- k})  - \ell^{-k}(\hat{\beta}^{- k})$ and  $\ell^{k}(\hat{\beta}^{-k})$ are equivalent to each other -- in other words, the standard and V\&VH approaches agree.  However, Verweij and Van Houwelingen's approach is more stable for Cox regression as there is always a large number of observations in the risk sets its calculations are based on.  Since its proposal, the V\&VH approach has been widely implemented as a tool for cross-validation is Cox models.  For example, it is used by the R packages {\tt CoxRidge} \citep{CoxRidge}, {\tt fastcox} \citep{fastcox}, {\tt SGL}\citep{SGL} , {\tt CoxBoost}\citep{CoxBoost}, {\tt mboost}\citep{mboost}, and {\tt glmnet}\citep{glmnet}.  In {\tt glmnet}, it is the default choice for penalized Cox regression and is referred to as the {\tt grouped} option in the package's syntax.%\note{PB: I like the mention of these packages, but they need citations.}%\bnote{citation added}

@@

\par Both of the methods in Section~\ref{Sec:cox-cv-existing} consist of adding together partial likelihood measures from each fold.  An alternative method is to obtain linear predictors for each fold, then combine these linear predictors to calculate a partial likelihood. We refer to this method as the \emph{cross-validated linear predictors} approach. To be more specific, we would first obtain $\hat{\beta}^{-k}$ from training set $T_{k}$; then the cross-validated linear predictors can be calculated for each observation $i$ from the test set $D_k$:  
\begin{equation}
  \label{eq:cv-lp}
  \hat{\eta}^{cv}_{i} = X_{i}\hat{\beta}^{-k}
\end{equation} 
After repeating this for all K folds, a complete set of cross-validated linear predictors $\hat{\eta}^{cv} = ( \hat{\eta}^{cv}_{1},  \hat{\eta}^{cv}_{2} , ...  \hat{\eta}^{cv}_{n})$ for the whole sample is obtained. A partial likelihood can then be built over this set of linear predictors to evaluate the predictive accuracy of the model: 
	\begin{equation} 
	L(\hat{\eta}^{cv}) = \prod_{i=1}^{n} \frac{\exp (\hat{\eta}^{cv}_{i})}{\sum_{ j \in R(t_{i})}\exp (\hat{\eta}^{cv}_{j})}.
	\end{equation}
%\note{BIYUE: Throughout, use $\log$ instead of $log$, $\exp$ instead of $exp$, and $\ell$ instead of $l$.}
We define the cross-validation error evaluated with cross-validated linear predictors to be $$\CVE = - \log L(\hat{\eta}^{cv}).$$

@@

  % \begin{figure}[h]
    %\centering
    %\begin{minipage}[b]{0.45\textwidth}
      %\centering
	%	  \includegraphics[height= 3.9cm ]{./figures/03.png}
      %\caption{CV Linear Predictors}
     %\end{minipage}
     %\begin{minipage}[b]{0.45\textwidth}
      %\centering
%		  \includegraphics[height= 4.1cm ]{./figures/04_2.png}
    %  \caption{CV Deviance Residuals}
     % \end{minipage}	
  % \end{figure}

@@

\begin{figure}
  \centering
		\includegraphics[height= 12cm ]{./figures/figure_1_new.png}
%		%\includegraphics[height= 4cm ]{./figures/02_2.png}
   \caption{Illustration of K-fold Cross Validation Methods for Cox Regression}
\end{figure}

@@

Simulation studies were conducted to compare how those methods behave relative to each other in selecting the tuning parameter $\lambda$ and the corresponding model for LASSO penalized regression. Survival times were generated from exponential distribution $h(t) = h_{0} \exp(X\beta)$, where $h_{0}$ is the prespecified baseline; $X$ is the covariate matrix generated from independent $\text{Normal}(0, 1)$ with $n$ observations and $p$ covariates; and $\beta$, the coefficients of the true model, is a vector whose majority entries are set to be 0 to guarentee sparsity. Censoring status were generated based on an independent binomial distribution. All simulations were implemented in R \citep{R}.

We first studied the accuracy of the models via several in-sample and out-of-sample measures. We varied the sample size, dimension, censoring percentage and signals of the simulated data sets to examine how those factors would affect the model selected via those cross-validation approaches. We also conducted a simulation study to examine the stability issue of the standard approach. Finally, we extended the comparison from K-fold cross-validation to Leave One Out Cross-validation (LOOCV).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \subsection {Simulations Comparing Predictive Accuracy}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\par The first sets of simulation studies were conducted to study the predictive accuarcy of the model selected by the forementioned cross-validation approaches. We compared the predictive accuracy of the selected model via several distinct criteria.

\par We first measure the distance between the fitted model and the true model via mean squared error of the coefficients. Suppose $\hat{\beta}(\lambda)$ is the set of coefficients estimated by a cox model with LASSO penalty at $\lambda$. Mean squared error $MSE$ is defined to be 
\begin{equation}
E(\hat{\beta}(\lambda) - \beta)^2
\end{equation}
For each generated data set, an oracle model would be fitted using Cox regression only upon variables that are set as non-zero in the data generating process. The resulted estimates would be denoted by $\hat{\beta}^{oracle}$. Then the models selected by the cross validation methods with $\lambda^{cv}$ would be compared to the oracle model via 
\begin{equation}
\log\left\{ \frac{MSE(\hat{\beta}(\lambda^{\text{cv}}))}{MSE(\hat{\beta}^{\text{oracle}})} \right\}
\end{equation}
for each cross-validation selected $\lambda^{cv}$ in each generated data set. The results would be averaged over N replications. We take $log$ of the MSE ratio to correct the right skewness.

@@

\par We also measure the predictive accuracy via Brier score, which can be interpreted as the mean squared error of the prediction \citep{VanHouwelingen2011}. Suppose $\hat{S}(t_0|\lambda,x)$ is the prediction of survival probability of an individual beyond time $t_0$ with covariate $x$ based on model $\hat{\beta}(\lambda)$. Suppose the actual observation is defined as $y = \mathbb{1}(\left\{ t > t_{0}\right\})$, which is an indicator of whether the event is observed after $t_0$ or not. Then the Brier score is defined to be:
\begin{equation}
	\text{Brier}(y, \hat{S}(t_0|\lambda,x)) = (y - \hat{S}(t_0|\lambda,x))^2
\end{equation}
In our simulations, for each generated data set, we generated another independent data set that has 1000 observations without censoring. We computed Brier Scores upon all individuals in this independent test set where $t_0$ is set to be the median survival time for all four models selected by cross-validation. Lower Brier Scores means smaller prediction error, thus indicating better prediction accuracy.

\par The third measure we used is the Kullback-Leibler score, which measures the log-likelihood of the prediction model evaluated at the observations \citep{VanHouwelingen2011}. With the same notation defined in the previous paragraph, the Kullback-Leibler score is defined to be:
\begin{equation}
	\text{KL}(y, \hat{S}(t_0|\lambda,x)) = -\left\{ y\log(\hat{S}(t_0|\lambda,x) + (1 - y)\log(1 - \hat{S}(t_0|\lambda,x)) \right\}
\end{equation}
We computed KL score upon individuals in the independent test set at their median survival time for all four models selected by cross-validation. Results were then averaged over the N replications. Lower KL Scores means smaller discrepency between the selected model and the true model, thus indicating better prediction accuracy.

\par While the MSE, Brier Score and Kullback-Leibler Score are good measures of the model, they are not very interpretable. Hence, we included Harrell's C Index as the last measure of the predictive accuracy\citep{HarrellJr1984}. The C Index is a rank-based statistic that measures the concordance between the linear predictor of the selected model and the observed outcome. Suppose we arbitrarily take two observation out of the data. If the observation that has a greater prognostic score also has a greater risk or shorter survival time until the event occur, then this would be considered as a concordant pair. C Index estimates of proportion of concordance pairs in the data set. C Index of 0.5 means the prediction is as good as flipping a coin and C Index of 1 means perfect concordance. We also computed Harrell's C Index upon the independent test set for all four models selected by cross-validation and averaged over all replications.

The simulation experiments were first conducted when the signal in the data was varied. In each simulated data set, there are n = 120 observations and p = 1000 covariates. 10$\%$ of the observations were censored. 10-fold cross-validation was implemented for all four methods. Number of non-zero $\beta$s was 10. The signal in the data set was varied by varying the magnitude of the $\beta$s from 0.4 to 0.9. For each scenario, 200 replications were used.

\begin{figure}[h]
    \centering
		\includegraphics[height= 7cm ]{./figures/figure_2_new.png}
    \caption{Simulation Studies Comparing 4 CV methods in terms of $\lambda$ and MSE ratio. n = 150, p = 1000, 10$\%$ censoring.}
\end{figure}

@@

\par Results of the simulation were illustrated in Figure 2. The x axis of the plots are the magnitude of the non-zero $\beta$ coefficients. The left panel compares the MSE ratios of selected models.  The y-axis represents the MSE ratios between the cross-validation selected models and the oracle model. The standard method has the smallest MSE ratio. The linear predictor approach's performance is also very close the standard approach. Both Verweij and Van Houwelingen's approach and the proposed deviance residual approach yield models that have greater MSE. The middle panel compares the Brier scores of the models selected. The y-axis represents the Brier score. The standard method and the linear predictor approach have lower brier score across all levels of signals. Both Verweij and Van Houwelingen's approach and the proposed deviance residual approach yield models that have greater Brier scores. The left panel compares Harrell's C of the models selected. The y-axis represents Harrell's C, which increases from around 0.6 to 0.8 as the coefficent size increases. The standard method and the linear predictor approach have slightly higher Harrell's C across all levels of signals, indicating better prediction accuracy. Overall, all four methods have very close performance .

\begin{table}[h]

@@

\caption{\label{tab:} Simulation Studies that Compare All Four Cross-Validation Methods Varying Dimension and Signal }
\centering
\begin{tabular}[t]{cccccccccc}
\toprule
 n& p& $\#$ Non-Zero & Signal & Method & $\lambda$ & log(MSE Ratio) &Brier Score & Kullback Leibler & C Index\\
\midrule
150 & 50 & 5 & low & V VH  & 0.095 (0.028) & 1.457 (0.954) & 0.242 (0.013) & 0.678 (0.029) & 0.617 (0.034) \\
    &    &   &     & Standard  & 0.087 (0.030) & 1.459 (0.922) & 0.242 (0.013) & 0.678 (0.029) & 0.618 (0.032) \\
    &    &   &     & LinearPred  & 0.088 (0.025) & 1.433 (0.927) & 0.241 (0.013) & 0.677 (0.028) & 0.620 (0.029) \\
    &    &   &     & DevResid  & 0.132 (0.032) & 1.676 (1.019) & 0.248 (0.014) & 0.689 (0.030) & 0.601 (0.044) \\
\addlinespace
150 & 50 & 5 & strong & V VH  & 0.070 (0.011) & 1.733 (0.922) & 0.177 (0.012) & 0.527 (0.030) & 0.750 (0.014) \\
    &    &   &     & Standard  & 0.066 (0.012) & 1.688 (0.909) & 0.176 (0.012) & 0.526 (0.029) & 0.749 (0.014) \\
    &    &   &     & LinearPred  & 0.067 (0.011) & 1.695 (0.925) & 0.176 (0.012) & 0.526 (0.030) & 0.750 (0.014) \\
    &    &   &     & DevResid  & 0.110 (0.012) & 2.339 (0.868) & 0.187 (0.014) & 0.554 (0.033) & 0.750 (0.018) \\
\addlinespace
300 & 10000 & 20 & low & V VH  & 0.139 (0.021) & 3.463 (0.438) & 0.244 (0.015) & 0.681 (0.032) & 0.612 (0.051) \\
    &    &   &     & Standard  & 0.105 (0.027) & 3.350 (0.458) & 0.228 (0.021) & 0.646 (0.045) & 0.639 (0.05) \\
    &    &   &     & LinearPred  & 0.107 (0.026) & 3.360 (0.462) & 0.229 (0.021) & 0.648 (0.045) & 0.638 (0.049) \\
    &    &   &     & DevResid  & 0.139 (0.027) & 3.454 (0.447) & 0.243 (0.018) & 0.678 (0.038) & 0.610 (0.058) \\
\addlinespace
500 & 10000 & 20 & strong & V VH  & 0.072 (0.005) & 3.469 (0.480) & 0.162 (0.015) & 0.495 (0.036) & 0.784 (0.021) \\
    &    &   &     & Standard  & 0.056 (0.005) & 3.174 (0.504) & 0.153 (0.011) & 0.465 (0.029) & 0.782 (0.017) \\
    &    &   &     & LinearPred  & 0.057 (0.005) & 3.204 (0.498) & 0.153 (0.011) & 0.466 (0.029) & 0.783 (0.017) \\
    &    &   &     & DevResid  & 0.076 (0.005) & 3.545 (0.467) & 0.167 (0.015) & 0.508 (0.035) & 0.782 (0.022) \\
\bottomrule
\end{tabular}
\end{table}

\par Additional simulation studies were conducted for other four scenarios, which are a combination of different dimensions and signal in the data. The results are shown in Table 1. More specifically, we examined low dimension (p = 50) with weak signal, low dimension with strong signal, high dimension (p = 10000) with weak signal and high dimension with strong signal. Censoring was set to be 30$\%$. Overall, the standard approach and linear predictor approach tend to select smaller $\lambda$ and select more variables than the other two approaches. Among all four of them, the Deviance residual approahc is the most conservative one.

\par Scenarios with higher signal and lower dimensions are considered as easier scenarios to select the most predictive model. As is shown in the results, at p = 10000 with weak signal, which is the hardest scenario, the standard approach and the linear predictor approach have the greatest advantage. They out-performed the other two methods in all predictive measures. The differences in performance are neglegible at low dimension or when there is strong signal in the data.

>>>>

\note{What's with all the \textbackslash par commands?  They don't seem to do anything.}

@@

%%%%%%%%%%%%%
%%%%%%%%%%%%%
\section{Methods}
\label{Sec:methods}
%%%%%%%%%%%%%
%%%%%%%%%%%%%

@@

To address this issue, \citet{Verweij1993} proposed an alternative method for cross-validation in Cox models:
\begin{equation}
\label{eq:VVH}
	\CVE = -2\sum_{k = 1}^K \left\{ \ell(\hat{\beta}^{- k})  - \ell^{-k}(\hat{\beta}^{- k}) \right\}. 
\end{equation}
Here, $\ell(\hat{\beta}^{-k})$ is the log partial likelihood evaluated at $\hat{\beta}^{-k}$ using the entire data set $D$ and $\ell^{-k}(\hat{\beta}^{-k})$ is the log partial likelihood evaluated at $\hat{\beta}^{-k}$ on
the training set $T_k$. By avoiding the construction of a partial likelihood on the test set, this approach ensures that the risk set is always sufficiently large and the partial likelihood well-defined.  We refer to this cross-validation method as the Verweij and Van Houwelingen (V\&VH) approach. For many models, such as logistic regression or linear regression, the quantities $\ell(\hat{\beta}^{- k})  - \ell^{-k}(\hat{\beta}^{- k})$ and  $\ell^{k}(\hat{\beta}^{-k})$ are equivalent to each other -- in other words, the standard and V\&VH approaches agree.  However, Verweij and Van Houwelingen's approach is more stable for Cox regression as there is always a large number of observations in the risk sets its calculations are based on.  Since its proposal, the V\&VH approach has been widely implemented as a tool for cross-validation is Cox models.  For example, it is used by the R packages {\tt CoxRidge} \citep{CoxRidge}, {\tt fastcox} \citep{fastcox}, {\tt SGL}\citep{SGL} , {\tt CoxBoost}\citep{CoxBoost}, {\tt mboost}\citep{mboost}, and {\tt glmnet}\citep{glmnet}.  In {\tt glmnet}, it is the default choice for penalized Cox regression and is referred to as the {\tt grouped} option in the package's syntax.

@@

\par Both of the methods in Section~\ref{Sec:cox-cv-existing} consist of adding together partial likelihood measures from each fold.  An alternative method is to obtain linear predictors for each fold, then combine these linear predictors to calculate a partial likelihood. We refer to this method as the \emph{cross-validated linear predictors} approach. To be more specific, we would first obtain $\hat{\beta}^{-k}$ from training set $T_{k}$; then the cross-validated linear predictors can be calculated for each observation $i$ from the test set $D_k$:  
\begin{equation}
  \label{eq:cv-lp}
  \hat{\eta}^{cv}_{i} = X_{i}\hat{\beta}^{-k}
\end{equation} 
After repeating this for all K folds, a complete set of cross-validated linear predictors $\hat{\eta}^{cv} = ( \hat{\eta}^{cv}_{1},  \hat{\eta}^{cv}_{2} , ...  \hat{\eta}^{cv}_{n})$ for the whole sample is obtained. A partial likelihood can then be built over this set of linear predictors to evaluate the predictive accuracy of the model: 
	\begin{equation} 
	L(\hat{\eta}^{cv}) = \prod_{i=1}^{n} \frac{\exp (\hat{\eta}^{cv}_{i})}{\sum_{ j \in R(t_{i})}\exp (\hat{\eta}^{cv}_{j})}.
	\end{equation}
We define the cross-validation error evaluated with cross-validated linear predictors to be $$\CVE = - 2 \log L(\hat{\eta}^{cv}).$$

@@

@@

\begin{figure}
  \centering
  \includegraphics[height= 12cm ]{./figures/figure_1_new.png}
  \caption{Illustration of K-fold Cross Validation Methods for Cox Regression}
\end{figure}

@@

Simulation studies were conducted to compare how those methods behave relative to each other in selecting the tuning parameter $\lambda$ and the corresponding model for LASSO penalized regression. Survival times were generated from exponential distribution $h(t) = h_{0} \exp(X\beta)$, where $h_{0}$ is the prespecified baseline\note{huh?  so what is $h_0$?}; the covariate matrix $X$ with $n$ observations and $p$ covariates is generated from independent $\text{Normal}(0, 1)$ samples; and the coefficient vector $\beta$ is sparse, with most entries equal to zero. Censoring status indicators were drawn independently from the binomial distribution. All simulations were implemented in R \citep{R}. We varied the sample size, dimension, censoring percentage and signal strength of the simulated data sets to examine how these factors affect the performance of cross-validation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection {Simulations Comparing Predictive Accuracy}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Our first simulation study concerns the accuracy of the cross-validation approaches introduces in Section~\ref{Sec:methods}.  Accuracy was assesed via several criteria.

Estimation accuracy was measured using the mean squared error of the coefficients ($\MSE$). Suppose $\hat{\beta}(\lambda)$ is the set of coefficients estimated by a cox model with LASSO penalty at $\lambda$. Mean squared error $MSE$ is defined to be 
\begin{equation}
E(\hat{\beta}(\lambda) - \beta)^2.
\end{equation}
\note{this is the equation for a scalar MSE, not a vector}

Throughout, we communicate the estimation accuracy in terms of relative MSE, as compared to the oracle model.  For each generated data set, an oracle model was fit using Cox regression only including the variables with non-zero coefficients. Letting $\hat{\beta}^{oracle}$ denote the resulting estimates, the relative MSE, on the log scale, is given by
\begin{equation}
\log\left\{ \frac{\MSE(\hat{\beta}(\lambda^{\text{cv}}))}{\MSE(\hat{\beta}^{\text{oracle}})} \right\},
\end{equation}
where $\lambda^{cv}$ denotes the value of $\lambda$ selected by cross-validation.   These results are then averaged over N replications; the $\log$ of the ratio is taken to correct for skewness.

@@

\par We also measure the predictive accuracy via the mean squared prediction error, or Brier score \citep{VanHouwelingen2011}. Let $\hat{S}(t_0|\lambda,x)$ denote the predicted probability for an individual with covariates $x$ to survive beyond time $t_0$, and let $y = \mathbb{1}\left\{ t > t_{0}\right\}$ indicate whether the individual actually survived beyond time $t_0$. Then the Brier score is defined to be
\begin{equation}
\text{Brier}(y, \hat{S}(t_0|\lambda,x)) = (y - \hat{S}(t_0|\lambda,x))^2.
\end{equation}
In our simulation study, for each data set, we generated another independent data set with 1000 uncensored observations. We computed Brier scores for all of the cross-validation methods for all individuals in this test set, setting $t_0$ to the median survival time.

\par The third measure we used is the Kullback-Leibler score, which measures the log-likelihood of the prediction model evaluated at the observations \citep{VanHouwelingen2011}. With the same notation defined in the previous paragraph, the Kullback-Leibler score is defined to be
\begin{equation}
	\text{KL}(y, \hat{S}(t_0|\lambda,x)) = -\left\{ y\log(\hat{S}(t_0|\lambda,x) + (1 - y)\log(1 - \hat{S}(t_0|\lambda,x)) \right\}.
\end{equation}
As for the Brier score, KL scores were computed for all CV approaches at the median survival time.  Results were then averaged over the N replications. For both Brier and KL scores, a score represents smaller prediction error, thus indicating better prediction accuracy.

\par The final metric we included in our study was Harrell's C Index \citep{HarrellJr1984}. The C Index is a rank-based statistic that measures the concordance between the linear predictor of the selected model and the observed outcome. Suppose we arbitrarily select two individuals; if the individual with the higher predicted risk also died first, then this would be considered as a concordant pair. The C Index considers all possible such pairs and estimates of proportion of those pairs that are concordant. A C Index of 0.5 means the prediction is no better than flipping a coin and C Index of 1 means perfect concordance. We computed Harrell's C Index using the independent test set of 1000 individuals described above.

For each simulated data set, there were $n = 120$ observations, $p = 1000$ covariates. and 10\% of the observations were censored. For each of the four methods described in Section~\ref{Sec:methods}, 10-fold cross-validation was implemented. Number of non-zero $\beta$s was 10. The signal in the data set was varied by varying the magnitude of the $\beta$s from 0.4 to 0.9. \note{Would it be better here to descibe the $\beta$ values explicitly, with an equation?} For each scenario, 200 replications were used.

\begin{figure}[ht]
  \centering
  \includegraphics[height= 7cm ]{./figures/figure_2_new.png}
  \caption{\label{Fig:mse-brier-c} Simulation comparing 4 CV methods in terms of $\lambda$ and MSE ratio (relative to the oracle model) \note{UPDATE CAPTION}. n = 150, p = 1000, 10$\%$ censoring.}
\end{figure}

@@

\par Figure~\ref{Fig:mse-brier-c} illustrates the results of this simulation study. In each panel, the horizontal axis is the magnitude of the non-zero $\beta$ coefficients.  For all four metrics, the overall pattern is the same (KL scores not shown in Figure~\ref{Fig:mse-brier-c} due to space constraints, but they were very similar to Brier scores).  Although the four cross-validation methods performed relatively similarly, the standard and linear predictor approaches had the best performance across all metrics: lower MSE, better Brier scores, and higher concordance.

\begin{table}[htb]

@@

\caption{\label{Tab:sim} Simulation comparing four cross-validation methods with varying dimension and signal strength}
\centering
\begin{tabular}[t]{cccccccccc}
\toprule
 n& p& $\#$ Non-Zero & Signal & Method & $\lambda$ & log(MSE Ratio) &Brier Score & Kullback Leibler & C Index\\
\midrule
150 & 50 & 5 & low & V VH  & 0.095 (0.028) & 1.457 (0.954) & 0.242 (0.013) & 0.678 (0.029) & 0.617 (0.034) \\
    &    &   &     & Standard  & 0.087 (0.030) & 1.459 (0.922) & 0.242 (0.013) & 0.678 (0.029) & 0.618 (0.032) \\
    &    &   &     & LinearPred  & 0.088 (0.025) & 1.433 (0.927) & 0.241 (0.013) & 0.677 (0.028) & 0.620 (0.029) \\
    &    &   &     & DevResid  & 0.132 (0.032) & 1.676 (1.019) & 0.248 (0.014) & 0.689 (0.030) & 0.601 (0.044) \\
\addlinespace
150 & 50 & 5 & strong & V VH  & 0.070 (0.011) & 1.733 (0.922) & 0.177 (0.012) & 0.527 (0.030) & 0.750 (0.014) \\
    &    &   &     & Standard  & 0.066 (0.012) & 1.688 (0.909) & 0.176 (0.012) & 0.526 (0.029) & 0.749 (0.014) \\
    &    &   &     & LinearPred  & 0.067 (0.011) & 1.695 (0.925) & 0.176 (0.012) & 0.526 (0.030) & 0.750 (0.014) \\
    &    &   &     & DevResid  & 0.110 (0.012) & 2.339 (0.868) & 0.187 (0.014) & 0.554 (0.033) & 0.750 (0.018) \\
\addlinespace
300 & 10000 & 20 & low & V VH  & 0.139 (0.021) & 3.463 (0.438) & 0.244 (0.015) & 0.681 (0.032) & 0.612 (0.051) \\
    &    &   &     & Standard  & 0.105 (0.027) & 3.350 (0.458) & 0.228 (0.021) & 0.646 (0.045) & 0.639 (0.05) \\
    &    &   &     & LinearPred  & 0.107 (0.026) & 3.360 (0.462) & 0.229 (0.021) & 0.648 (0.045) & 0.638 (0.049) \\
    &    &   &     & DevResid  & 0.139 (0.027) & 3.454 (0.447) & 0.243 (0.018) & 0.678 (0.038) & 0.610 (0.058) \\
\addlinespace
500 & 10000 & 20 & strong & V VH  & 0.072 (0.005) & 3.469 (0.480) & 0.162 (0.015) & 0.495 (0.036) & 0.784 (0.021) \\
    &    &   &     & Standard  & 0.056 (0.005) & 3.174 (0.504) & 0.153 (0.011) & 0.465 (0.029) & 0.782 (0.017) \\
    &    &   &     & LinearPred  & 0.057 (0.005) & 3.204 (0.498) & 0.153 (0.011) & 0.466 (0.029) & 0.783 (0.017) \\
    &    &   &     & DevResid  & 0.076 (0.005) & 3.545 (0.467) & 0.167 (0.015) & 0.508 (0.035) & 0.782 (0.022) \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{Tab:sim} displays the results of additional simulations carried out as we varied the dimension of the data set along with the signal strength.  Specifically, we examined the following settings: low dimension (p = 50) with weak signal, low dimension with strong signal, high dimension (p = 10000) with weak signal, and high dimension with strong signal. In all settings, the censoring rate was 30\%.

As in Figure~\ref{Fig:mse-brier-c}, the standard and linear predictor approaches outperform the deviance residual and $V\&VH$ approaches.  The improvement is particularly noticeable in the most difficult setting: high-dimensional data with weak signal.  Table~\ref{Tab:sim} also provides some insight into why the deviance residual and $V\&VH$ approaches perform poorly relative to standard CV and the linear predictor approach: they act conservatively, consistently choosing larger $\lam$ values and selecting fewer variables. \note{if we're going to say something about ``selecting fewer variables'', should Table 1 include the average model size?}
